Studies of quantum dots

### 2016-08-01 Manuscript/paper.tex
Update spEnergiesQD/Manuscript/paper.tex

In the similarity renormalization group (SRG) method, one performs a
continuous sequence of unitary transformations on a Hamiltonian operator
$\hat H$ to evolve it into a more ``amenable'' form -- which generally implies
decoupling a small model space of interest from its complement.  The sequence
is parameterized by a continuous variable $s$ known as the \textit{flow
  parameter}, which by convention we define to be $0$ at the beginning of the
sequence.  Upon reaching $s$, the transformed Hamiltonian is given by
\begin{align*}
  \tilde H(s) \equiv \hat U(s) \hat H \hat U(s)
\end{align*}
where $U(s)$ describes the product of all such transformations since $s = 0$.
At every step $s'$, the differential unitary transformation is described by
the exponential of an antihermitian operator $\eta(s)$, known as the
\textit{generator} of the transformation.  When ``integrated'' as a product,
the full transformation $\hat U(s)$ is recovered:\footnote{Alternatively, this
  can also be reinterpreted as an $s'$-ordered integral.  See \cite[\S
  6.1]{reimann2013quantum}.}
\begin{align*}
  \hat U(s) = \lim_{\Delta s' \to 0} \prod_{s' = 0}^{s' = s}
  \mathrm e^{\hat \eta(s') \Delta s'}
\end{align*}
The evolution of the Hamiltonian itself is governed by a differential
equation, commonly referred to as the flow equation:
\begin{gather} \label{eq:imsrgode}
  \frac{d}{d s} \tilde H(s) = [\hat \eta(s), \tilde H(s)]
\end{gather}
which allows $\tilde H(s)$ to be evaluated without explicitly constructing the
full transformation $\hat U(s)$.

 Introducing a flow parameter $s$, there exits a unitary
 transformation $U_s$, such that
\begin{equation}
 \hat{H}_s = U_s^\dagger \hat{H} U_s \equiv \Hd_s + \Ho_s,
\end{equation}
with the relations $U_{s=0} = \mathbf{1}$, and $\hat{H}_{s= 0} =
\hat{H}$.  The transformation $U_s$ is parametrized as
\[
U_s = T_s \exp \left(\int_0^s \! ds'\hat{\eta}_{s'} \right),
\]
where the anti-hermitian operator $\hat{\eta}_s$ serves as generator
of the transformation. With $T_s$ we denote $s$-ordering, which is
defined equivalently to usual time-ordering.  Taking the derivative of
$\hat{H}_s$ with respect to $s$ gives
\begin{equation}
 \frac{d \hat{H}_s}{ds} = \frac{d U_s}{ds}\hat{H} U_s^\dagger + U_s
 \hat{H} \frac{d U_s^\dagger}{ds}.
\label{eq:flow_long}
\end{equation}
Utilizing that for our particular form of $U_s$, we have that \be
\hat{\eta}_s = \frac{d U_s}{ds} U_s^\dagger = - U_s \frac{d
  U_s^\dagger}{ds} = -\hat{\eta}_s,
\label{eq:eta}
\ee we obtain that \be \frac{d \hat{H}_s}{ds} = \hat{\eta}_s \hat{H}_s
- \hat{H}_s \hat{\eta}_s = \left[\hat{\eta}_s, \hat{H}_s \right].
\label{eq:flowEquations}
\ee This is the key expression of the SRG method, describing the flow
of the Hamiltonian.  The specific unitary transformation is determined
by the choice of $\hat{\eta}_s$.  Through different choices of
$\hat{\eta}_s$, the SRG evolution can be adapted to the features of a
particular problem.\\

>>>>

In the similarity renormalization group (SRG) method, one performs a
continuous sequence of unitary transformations on a Hamiltonian operator
$\hat H$ to evolve it into a more ``amenable'' form -- which generally implies
decoupling a small model space of interest from its complement.  The sequence
is parameterized by a continuous variable $s$ known as the \textit{flow
  parameter}, which by convention we define to be $0$ at the beginning of the
sequence.  Upon reaching $s$, the transformed Hamiltonian is given by
\begin{align*}
  \tilde H(s) \equiv \hat U(s) \hat H \hat U(s)
\end{align*}
where $U(s)$ describes the product of all such transformations since $s = 0$.
At every step $s'$, the differential unitary transformation is described by
the exponential of an antihermitian operator $\eta(s)$, known as the
\textit{generator} of the transformation.  When ``integrated'' as a product,
the full transformation $\hat U(s)$ is recovered:\footnote{Alternatively, this
  can also be reinterpreted as an $s'$-ordered integral.  See \cite[\S
  6.1]{reimann2013quantum}.}
\begin{align*}
  \hat U(s')
  = \mathcal T_s \left\{ \exp \left(\int_0^{s'} \hat \eta_s \, d s \right)\},
  := \lim_{\Delta s \to 0} \prod_{s = 0}^{s = s'}
  \mathrm e^{\hat \eta(s) \Delta s}
\end{align*}
where $\mathcal T_s$ denotes $s$-ordering, defined analogously to the usual
time-ordering from quantum field theory.

The evolution of the Hamiltonian itself is governed by a differential
equation, commonly referred to as the flow equation:
\begin{gather} \label{eq:imsrgode}
  \frac{d}{d s} \tilde H(s) = [\hat \eta(s), \tilde H(s)]
\end{gather}
which allows $\tilde H(s)$ to be evaluated without explicitly constructing the
full transformation $\hat U(s)$.

 Introducing a flow parameter $s$, there exits a unitary
 transformation $U_s$, such that
\begin{equation}
 \hat{H}_s = U_s^\dagger \hat{H} U_s \equiv \Hd_s + \Ho_s,
\end{equation}
with the relations $U_{s=0} = \mathbf{1}$, and $\hat{H}_{s= 0} =
\hat{H}$.  The transformation $U_s$ is parametrized as
\[
U(s') = \mathcal T_s \left\{ \exp \left(\int_0^{s'} \! ds'\hat{\eta}_s \right)\},
\]
Taking the derivative of $\hat{H}_s$ with respect to $s$ gives
\begin{equation}
 \frac{d \hat H(s)}{d s} = \frac{d U(s)}{ds} \hat{H}(0) U^\dagger(s) + U(s)
 \hat{H} \frac{d U^\dagger(s)}{ds}.
\label{eq:flow_long}
\end{equation}
Utilizing that for our particular form of $U(s)$, we have that \be
\hat{\eta}(s) = \frac{d U_s}{ds} U^\dagger(s) = - U(s) \frac{d U^\dagger(s)}{ds} = -\hat{\eta}(s),
\label{eq:eta}
\ee we obtain that \be \frac{d \hat{H}_s}{ds} = \hat{\eta}_s \hat{H}_s
- \hat{H}_s \hat{\eta}_s = \left[\hat{\eta}_s, \hat{H}_s \right].
\label{eq:flowEquations}
\ee This is the key expression of the SRG method, describing the flow
of the Hamiltonian.  The specific unitary transformation is determined
by the choice of $\hat{\eta}_s$.  Through different choices of
$\hat{\eta}_s$, the SRG evolution can be adapted to the features of a
particular problem.\\
